### 2018-12-12 reports/thesis/chapters/5_inference.tex
Started on simulated defect write up
Wrote about contaminated defected experiment
Line defect is 5 pixels thick in PlaneMultLine
Change alt mean to 3
Save figures for scripts in defectsimulation

\subsection{All Null Simulation}

An experiment was conducted to investigate how well the empirical null filter performs with no defects. The dataset \texttt{July 30deg} was used in this experiment.

The images in the dataset were spilt into two halves randomly. The mean over the first half of the images was taken and this was used as the ground truth, acting like an \texttt{aRTist} simulation. A smooth function was added to the ground truth to contaminate it and cause some systematic error. The idea was that the empirical null filter should do inference without being affected too much by the smooth function.

In the second half, all but one of the images were used in the training of the variance-mean model. The remaining image, the test image, was then used to compare with the simulated ground truth, producing a $z$ image. The $z$ image was then inferred using the empirical null filter and then the BH procedure.

The smooth functions investigated were a plane and a sinusoid. The harshness of the smooth functions were controlled using the gradient for the plane, and the amplitude for the sinusoid. The smooth functions are for the plane
\begin{equation}
	\delta\left[
		(x-x_0)+(y-y_0)
	\right]
\end{equation}
and the sinusoid
\begin{equation}
	A\sin\left[
		\dfrac{
			2\pi
		}
		{
			750
		}
		\left(
			(y-y_0)-(x-x_0)
		\right)
	\right]
\end{equation}
where $\delta$ is the gradient, $A$ is the amplitude and $(x_0,y_0)$ is the centre of the image.

Because no defects were implemented in this experiment, any positive results are false. The false positive rates were investigated for different harshness of the smooth functions. The experiment was repeated 20 times by randomly reallocating the images used for the ground truth, variance-mean training and testing.

Figures \ref{fig:inference_NoDefect_Plane_sigma} and \ref{fig:inference_NoDefect_Sinusoid_sigma} shows the false positive rate for the plane and sinusoid contamination respectively. For sensible varying functions, the empirical null filter did a good job of not being detecting the contamination as significant. In extreme cases it can be seen that false positives can happen and in particular when the smooth function is quite harsh and varies a lot spatially. This showed that the empirical null filter was not completely perfect and false positives can happen.

\begin{figure}
	\centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/NoDefect_Plane2sigma.eps}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/NoDefect_Plane3sigma.eps}
    \end{subfigure}
    }
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/NoDefect_Plane4sigma.eps}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/NoDefect_Plane5sigma.eps}
    \end{subfigure}
    }
    \caption{False positive rate when using the empirical null filter on an $z$ image where the ground truth was contaminated by a plane. Various $z_\alpha$ levels and gradients are shown.}
    \label{fig:inference_NoDefect_Plane_sigma}
\end{figure}

\begin{figure}
	\centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/NoDefect_Sinusoid2sigma.eps}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/NoDefect_Sinusoid3sigma.eps}
    \end{subfigure}
    }
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/NoDefect_Sinusoid4sigma.eps}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/NoDefect_Sinusoid5sigma.eps}
    \end{subfigure}
    }
    \caption{False positive rate when using the empirical null filter on an $z$ image where the ground truth was contaminated by a sinusoid. Various $z_\alpha$ levels and gradients are shown.}
    \label{fig:inference_NoDefect_Sinusoid_sigma}
\end{figure}

The spatial properties of the false positives did depend on the smooth function. Figures \ref{fig:inference_NoDefect_Plane_p_sig} and \ref{fig:inference_NoDefect_Sinusoid_p_sig} shows the location of the positive results for the plane and sinusoid contamination respectively. The $p$-values are also shown. These false positives are concerning as they are clustered together, giving false indication of a defect.

In practice, the amount of contamination won't be as harsh as the one demonstrated here. As long as the smooth function is slowly varying spatially, the empirical null filter will correct the test statistics accordingly.

\begin{figure}
	\centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/NoDefect_Plane_pvalues.eps}
        \caption{$\log p$-values}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/NoDefect_Plane_sig.eps}
        \caption{$z$ image with red significant pixels}
    \end{subfigure}
    }
    \caption{The $p$-values and significant pixels, at the $z_\alpha=2$ level, when using the empirical null filter on an $z$ image where the ground truth was contaminated by a plane with gradient 7.0.}
    \label{fig:inference_NoDefect_Plane_p_sig}
\end{figure}

\begin{figure}
	\centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/NoDefect_Sinusoid_pvalues.eps}
        \caption{$\log p$-values}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/NoDefect_Sinusoid_sig.eps}
        \caption{$z$ image with red significant pixels}
    \end{subfigure}
    }
    \caption{The $p$-values and significant pixels, at the $z_\alpha=2$ level, when using the empirical null filter on an $z$ image where the ground truth was contaminated by a sinusoid with amplitude $3\times10^3$.}
    \label{fig:inference_NoDefect_Sinusoid_p_sig}
\end{figure}

Figure \ref{fig:inference_NoDefect_nullmean} shows the estimated empirical null mean. It is remarkable that the empirical null mean recovers the smooth functions but artefacts from interpolation can be seen for the sinusoid contamination. The grid like structure in Figure \ref{fig:inference_NoDefect_Sinusoid_nullmean} shows that the estimated empirical null mean was not very smooth and more points should of been used to reduce the amount of interpolation, increasing the accuracy of the estimation.

\begin{figure}
	\centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/NoDefect_Plane_nullmean.eps}
        \caption{Plane, $\delta = 7.0$}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/NoDefect_Sinusoid_nullmean.eps}
        \caption{Sinusoid, $A=10^4$}
        \label{fig:inference_NoDefect_Sinusoid_nullmean}
    \end{subfigure}
    }
    \caption{Empirical null mean when using the empirical null filter on an $z$ image where the ground truth was contaminated by a smooth function.}
    \label{fig:inference_NoDefect_nullmean}
\end{figure}

These examples showed that the empirical null filter corrected the test statistics accordingly. However in extreme cases, the empirical null filter can fail and producing clusters of low $p$-values giving an illusion of a defect. In practice, extreme cases should not happen. Referring back to the real life example in Figure \ref{fig:inference_filter_mean_null}, the empirical null mean only varied around $0\pm3$ which is a small variation compared to Figure \ref{fig:inference_NoDefect_nullmean}.

\subsection{Defected Simulation}

An experiment was conducted to see if the empirical null filter detect defects under contamination. Just like the previous experiment, the dataset \texttt{July 30deg} was used. The images in the dataset were spilt, the mean of the first half acted as the ground truth, the rest were used to train the variance-mean model, one held out for testing. A plane with gradient $\delta=3$ was added to the ground truth to contaminate it. The contamination from the plane is quite mild following from the previous experiment.

Furthermore, defects were added to the ground truth by increasing selected pixels' grey values. Shapes such as squares and lines were used to simulate voids and cracks.

The receiver operating characteristic (ROC) curves \citep{green1966signal, metz1978basic, hanley1982meaning, friedman2001elements, cook2007use} were investigated. The ROC curve is a parametric plot, plotting the true positive rate against the false positive rate for varying thresholds. Other authors \citep{metz1978basic} use terminology such as sensitivity and specificity.

The area under the ROC curve is a commonly used statistic to quantify the performance of the test \citep{friedman2001elements}. Interpretations of the area do exist \citep{metz1978basic,hanley1982meaning} and discussed throughly in \cite{cook2007use}. The area under the ROC curve was recorded for different intensity values of the defect.

Figures \ref{fig:inference_SimulateRoc_Line_p_sig} and \ref{fig:inference_SimulateRoc_Squares_p_sig} shows the results of using the empirical null filter for inference. In this example an array of squares and a single vertical line were used to defect the ground truth by adding 298 to the grey value, a particularly small number. The defects were picked up which is remarkable. The structure of the false positives is quite similar to Figure \ref{fig:inference_NoDefect_Plane_p_sig}, indicating that the plane was still mildly harsh and responsible for the false positives.

The empirical null filter can fail if it treats a defect as the null. This can be mildly seen in Figure \ref{fig:inference_SimulateRoc_Squares_p_sig}, the top rows of square defects were not detected but the area outside the defect were tested as positive.

\begin{figure}
	\centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/SimulateRoc_Line_pvalues.eps}
        \caption{$-\log p$-values}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/SimulateRoc_Line_sig.eps}
        \caption{Image with significant pixels}
    \end{subfigure}
    }
    \caption{Hypothesis test using the empirical null filter on a simulated comparison. The ground truth was contaminated by a plane and defected by a single vertical line with value 298.}
    \label{fig:inference_SimulateRoc_Line_p_sig}
\end{figure}

\begin{figure}
	\centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/SimulateRoc_Squares_pvalues.eps}
        \caption{$-\log p$-values}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/SimulateRoc_Squares_sig.eps}
        \caption{Image with significant pixels}
    \end{subfigure}
    }
    \caption{Hypothesis test using the empirical null filter on a simulated comparison. The ground truth was contaminated by a plane and defected by an array of squares with value 298.}
    \label{fig:inference_SimulateRoc_Squares_p_sig}
\end{figure}

The ROC curves for different defect intensities are shown in Figures \ref{fig:inference_SimulateRoc_Lines_roc} and \ref{fig:inference_SimulateRoc_Squares_roc}. The dotted diagonal line show the ROC curve if the test classify each pixel randomly. Perfect classification happens on the top left of the graph when the true positive rate is one and the false positive rate is zero. A sample of ROC curves were obtained by reallocating the images to the ground truth, variance-mean training and testing, this was done 5 times.

\begin{figure}
	\centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/SimulateRoc_Line_roc_1.eps}
        \caption{Defect intensity = 100}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/SimulateRoc_Line_roc_7.eps}
        \caption{Defect intensity = 207}
    \end{subfigure}
    }
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/SimulateRoc_Line_roc_14.eps}
        \caption{Defect intensity = 483}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/SimulateRoc_Line_roc_20.eps}
        \caption{Defect intensity = 1000}
    \end{subfigure}
    }
    \caption{ROC curves when using the empirical null filter on a simulated comparison. The ground truth was contaminated by a plane and defected by an single vertical line. Each line represent a different fold when allocating images to the ground truth, variance-mean training and testing. This was done 5 times.}
    \label{fig:inference_SimulateRoc_Lines_roc}
\end{figure}

\begin{figure}
	\centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/SimulateRoc_Squares_roc_1.eps}
        \caption{Defect intensity = 100}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/SimulateRoc_Squares_roc_7.eps}
        \caption{Defect intensity = 207}
    \end{subfigure}
    }
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/SimulateRoc_Squares_roc_14.eps}
        \caption{Defect intensity = 483}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/SimulateRoc_Squares_roc_20.eps}
        \caption{Defect intensity = 1000}
    \end{subfigure}
    }
    \caption{ROC curves when using the empirical null filter on a simulated comparison. The ground truth was contaminated by a plane and defected by an array of squares. Each line represent a different fold when allocating images to the ground truth, variance-mean training and testing. This was done 5 times.}
    \label{fig:inference_SimulateRoc_Squares_roc}
\end{figure}

Figure \ref{fig:inference_SimulateRoc_roc_area} shows the area under the ROC curves for the single vertical line and array of squares defect. The areas were calculated using the trapezium rule. The results are promising with near perfect performance with defect intensities at least 600.

\begin{figure}
	\centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/SimulateRoc_Line_roc_area.eps}
        \caption{Line}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/SimulateRoc_Squares_roc_area.eps}
        \caption{Squares}
    \end{subfigure}
    }
    \caption{The area under the ROC curves for different defects and defect intensities. The ground truth was contaminated by a plane and defected. The experiment was repeated 5 times by reallocating images to the ground truth, variance-mean training and testing. The box plot represent those 5 repeats.}
    \label{fig:inference_SimulateRoc_roc_area}
\end{figure}

The experiments shows that the empirical null filter can correct the null distribution locally, giving better inference. In extreme cases, for example if the defect intensity is very small or the amount of contamination is rather large, the empirical null filter can fail. Harsh contamination can produce false positives because spatially rapidly changing grey values could be detected as a defect. The worst case would be that this would make defects appear to be the null, giving completely the opposite inference.

These extreme cases should not happen. As seen in the real life example at the start of the section, false positives are rare but they do have some spatial structure. If the defect intensity is too small to be detected, the contrast of the x-ray imaging apparatus should be adjusted to cater for it.

\subsection{Real Data}

There are ways to speed up the implementation of the empirical null filter by sacrificing accuracy. For example, instead of estimating the empirical null parameters for every pixel, a number of them can be estimated and then the remaining values can be interpolated. However it was found that interpolating $\widehat{\sigma}_{0,x,y}$ can yield highly varying results. To avoid this problem, it can be assumed that $\sigma_{0,x,y}=\sigma_0$ for all $x$ and $y$. Then the estimator $\widehat{\sigma}_0$ is the empirical null standard deviation estimator using all location corrected $z$ test statistics.

The empirical null filter was used on the example at the start of the chapter. It was used on a grid of $20\times 20$ points, the remaining values were interpolated. It was also assumed the empirical null standard deviation was constant, the methodology discussed in the previous paragraph.

The $z$ and $p$-value image, as shown in Figure \ref{fig:inference_filter_z_p_image}, now look more spatially uniform. The defects and some of the edges and corners are highlighted with their small $p$-values. In particular, Figure \ref{fig:inference_filter_z_ordered_p} shows that the test statistics look more Normal but with heavier tails. The heavier tails are contributed by non-null test statistics. Significant pixels are shown in Figure \ref{fig:inference_filter_sig_image}. It was encouraging to see less false positives and more defects being picked up. Because the BH procedure controls the FDR, some false positives are inevitable.

\begin{figure}
	\centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/filter_z_image.eps}
        \caption{$z$ image}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/filter_p_image.eps}
        \caption{$-\log p$-values}
    \end{subfigure}
    }
    \caption{The $z$ image and $p$-value image after using the empirical null filter.}
    \label{fig:inference_filter_z_p_image}
\end{figure}

\begin{figure}
	\centering
    \centerline{
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/filter_histogram.eps}
        \caption{Histogram of $z$ statistics}
    \end{subfigure}
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{../figures/inference/filter_p.eps}
        \caption{Ordered $p$ values}
    \end{subfigure}
    }
    \caption{Histogram of $z$ statistics and the corresponding ordered $p$-values when using the empirical null filter.}
    \label{fig:inference_filter_z_ordered_p}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=0.7\textwidth]{../figures/inference/filter_sig_image.eps}
	\caption{Using the empirical null filter, significant pixels were highlighted in red.} 
	\label{fig:inference_filter_sig_image}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=0.7\textwidth]{../figures/inference/filter_mean_null.eps}
	\caption{The estimated empirical null mean} 
	\label{fig:inference_filter_mean_null}
\end{figure}

In summary, the empirical null filter irons out each pixel in the $z$ image using the local mode. Figure \ref{fig:inference_filter_mean_null} shows the $\widehat{\mu}_{0,x,y}$ image, which varies a lot but smoothly. This demonstrated that by correcting the test statistics accordingly, sensible inference was achieved.

In the remaining of the chapter, properties of the empirical null filter were investigated.

>>>>

The study will now turn to contaminated defected images. Let $Z_{x,y}$ be the test statistics of pixel $(x,y)$ and under the null, it is distributed such that $Z_{x,y}|H_0\sim\normal(0,1)$. Defects refer to statistics which do not follow the null distribution, but instead an alternative distribution. For example it can be $Z_{x,y}|H_1\sim\normal(\mu_{1,x,y},1)$ and this example was used in this experiment. Contamination is a linear transform of the test statistics $Z_{x,y}$ such that
\begin{equation}
	C_{x,y} = Z_{x,y}\sigma_{0,x,y} + \mu_{0,x,y} \ .
\end{equation}
The empirical null filter recovers $Z_{x,y}$ from $C_{x,y}$. The values of the filtered test statistics are denoted as $\zeta_{x,y}$.

Various simulated defects were investigated. Dust defect with intensity $\pi_1$ assign all test statistics to be distributed such that
\begin{equation}
	p_{Z_{x,y}}(z)=(1-\pi_1)p_{Z_{x,y}|H_0}(z) + \pi_1 p_{Z_{x,y}|H_1}(z) \ .
\end{equation}
In other words, test statistics has the alternative distribution with probability $\pi_1$, and has the null distribution otherwise. This was chosen because the proportion of null statistics captured by a kernel should be independent of the radius of the kernel.

A line defect assign columns of pixels to have the alternative distribution, a kernel would only capture a section of defect. Similarly different shapes are used such as a square defect. With a square defect, a kernel can capture the entire defect.

\begin{figure}[p]
	\centering
		\centerline{
			\begin{subfigure}{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectDust_imagePreContaminated.eps}
				\caption{Uncontaminated}
			\end{subfigure}
			\begin{subfigure}{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectDust_imageContaminated.eps}
				\caption{Contaminated}
			\end{subfigure}
		}
		\centerline{
			\begin{subfigure}{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectDust_imageFiltered.eps}
				\caption{Filtered}
			\end{subfigure}
			\begin{subfigure}{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectDust_nullStd.eps}
				\caption{Empirical null std}
			\end{subfigure}
		}
	\caption{A $256 \times 256$ dust defect Gaussian image with/without contamination and after filtering with kernel radius 20. Defected pixels have the distribution $\normal(3,1)$. The dust defect has intensity $\pi_1 = 0.1$. The contamination is such that the null distribution is $Z_{x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$. Highlighted in red are significant pixels when controlling the FDR at the $2\sigma$ level.}
\end{figure}

\begin{figure}[p]
	\centering
		\centerline{
			\begin{subfigure}{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectLine_imagePreContaminated.eps}
				\caption{Uncontaminated}
			\end{subfigure}
			\begin{subfigure}{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectLine_imageContaminated.eps}
				\caption{Contaminated}
			\end{subfigure}
		}
		\centerline{
			\begin{subfigure}{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectLine_imageFiltered.eps}
				\caption{Filtered}
			\end{subfigure}
		}
	\caption{A $256 \times 256$ line defect Gaussian image with/without contamination and after filtering with kernel radius 20. Defected pixels have the distribution $\normal(3,1)$. The line is 5 pixels thick. The contamination is such that the null distribution is $Z_{x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$. Highlighted in red are significant pixels when controlling the FDR at the $2\sigma$ level.}
\end{figure}

\begin{figure}[p]
	\centering
		\centerline{
			\begin{subfigure}{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectSquare_imagePreContaminated.eps}
				\caption{Uncontaminated}
			\end{subfigure}
			\begin{subfigure}{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectSquare_imageContaminated.eps}
				\caption{Contaminated}
			\end{subfigure}
		}
		\centerline{
			\begin{subfigure}{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectSquare_imageFiltered.eps}
				\caption{Filtered}
			\end{subfigure}
			\begin{subfigure}{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectSquare_nullMean.eps}
				\caption{Empirical null mean}
			\end{subfigure}
		}
	\caption{A $256 \times 256$ square defect Gaussian image with/without contamination and after filtering with kernel radius 20. Defected pixels have the distribution $\normal(3,1)$. The square is $30\times 30$ pixels in size. The contamination is such that the null distribution is $Z_{x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$. Highlighted in red are significant pixels when controlling the FDR at the $2\sigma$ level.}
\end{figure}

\begin{figure}[p]
	\centering
		\centerline{
			\begin{subfigure}{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectSquare2_imagePreContaminated.eps}
				\caption{Uncontaminated}
			\end{subfigure}
			\begin{subfigure}{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectSquare2_imageContaminated.eps}
				\caption{Contaminated}
			\end{subfigure}
		}
		\centerline{
			\begin{subfigure}{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectSquare2_imageFiltered.eps}
				\caption{Filtered}
			\end{subfigure}
			\begin{subfigure}{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectSquare2_nullMean.eps}
				\caption{Empirical null mean}
			\end{subfigure}
		}
	\caption{A $256 \times 256$ square defect Gaussian image with/without contamination and after filtering with kernel radius 40. Defected pixels have the distribution $\normal(3,1)$. The square is $30\times 30$ pixels in size. The contamination is such that the null distribution is $Z_{x,y}\sim\normal(\mu_{0,x,y},\sigma_0^2)$ where $\mu_{0,x,y} = 0.01 (x-x_0) + 0.01 (y-y_0)$ and $\sigma_0=2$. Highlighted in red are significant pixels when controlling the FDR at the $2\sigma$ level.}
\end{figure}

\begin{figure}[p]
	\centering
		\centerline{
			\begin{subfigure}{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectDust_roc.eps}
				\caption{Dust defect $\pi_1=0.1$, $r=20$}
			\end{subfigure}
			\begin{subfigure}{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectLine_roc.eps}
				\caption{5 pixels thick line defect, $r=20$}
			\end{subfigure}
		}
		\centerline{
			\begin{subfigure}{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectSquare_roc.eps}
				\caption{$30\times 30$ square defect, $r=20$}
			\end{subfigure}
			\begin{subfigure}{0.49\textwidth}
				\includegraphics[width=\textwidth]{../figures/inference/defectsimulation/defectSquare2_roc.eps}
				\caption{$30\times 30$ square defect, $r=40$}
			\end{subfigure}
		}
	\caption{ROC}
\end{figure}
